Mechanical loading prediction though accelerometry data during walking and running

### 2021-05-15 manuscript/manuscript.Rmd
Minor corrections

**Purpose:** To develop accelerometry-based equations to predict peak ground reaction forces (pGRF) and peak loading rate (pLR) during walking and running. **Methods:** `r Words(max(sample_size$pGRF_N))` subjects (`r unname(sample_size_sex["F"])` females; `r sample_descriptives$body_mass_mean`±`r sample_descriptives$body_mass_sd` kg) walked and ran at different speeds (2–14km·h^-1^) on a force plate–equipped treadmill while wearing accelerometers at ankle, lower back and hip. Regression equations were developed to predict pGRF and pLR from accelerometry data. Leave-one-out cross-validation was used to calculate prediction accuracy and Bland–Altman plots. Our pGRF prediction equation was compared with a reference equation previously published. **Results:** Body mass and peak acceleration were included for pGRF prediction and body mass and peak acceleration rate for pLR prediction. All pGRF equation coefficients of determination were above `r myround(max(GRF_accuracy$R2_cond), 2)`, and a good agreement between actual and predicted pGRF was observed, with a mean absolute percent error (MAPE) below `r myround(max(GRF_accuracy$MAPE) * 100, 1)`\%. Accuracy indices from our equations were better than previously developed equations, with a MAPE 2 to 3 times better. All pLR prediction equations presented a lower accuracy compared to those developed to predict pGRF. **Conclusion:** Walking and running pGRF can be predicted with high accuracy by accelerometry-based equations, representing an easy way to determine mechanical loading in free-living conditions. The pLR prediction equations yielded an unsatisfactory accuracy. **Key Words:** ACTIVITY MONITOR, FORCE PLATES, LOCOMOTION, RAW ACCELERATION, MECHANICAL LOADING.

@@

A convenience sample of `r max(sample_size$pGRF_N)` adults (`r unname(sample_size_sex["M"])` males; `r sample_descriptives$age_mean`±`r sample_descriptives$age_sd` years; `r sample_descriptives$height_mean`±`r sample_descriptives$height_sd` cm; `r sample_descriptives$body_mass_mean`±`r sample_descriptives$body_mass_sd` kg; `r sample_descriptives$BMI_mean`±`r sample_descriptives$BMI_sd` kg·m^-2^, X̄±SD) with no self-reported neurological or musculoskeletal limitations was recruited. Height and body mass were assessed following standard procedures with a stadiometer and a digital scale, respectively. All participants were informed about the experiments purpose and protocol before giving written informed consent. The study was approved by the local Ethics Committee (CES 192-14).

>>>>

**Purpose:** To develop accelerometry-based equations to predict peak ground reaction forces (pGRF) and peak loading rate (pLR) during walking and running. **Methods:** `r max(sample_size$pGRF_N)` subjects (`r unname(sample_size_sex["F"])` females; `r sample_descriptives$body_mass_mean`±`r sample_descriptives$body_mass_sd` kg) walked and ran at different speeds (2–14km·h^-1^) on a force plate–equipped treadmill while wearing accelerometers at ankle, lower back and hip. Regression equations were developed to predict pGRF and pLR from accelerometry data. Leave-one-out cross-validation was used to calculate prediction accuracy and Bland–Altman plots. Our pGRF prediction equation was compared with a reference equation previously published. **Results:** Body mass and peak acceleration were included for pGRF prediction and body mass and peak acceleration rate for pLR prediction. All pGRF equation coefficients of determination were above `r myround(min(GRF_accuracy$R2_cond), 2)`, and a good agreement between actual and predicted pGRF was observed, with a mean absolute percent error (MAPE) below `r myround(max(GRF_accuracy$MAPE) * 100, 1)`\%. Accuracy indices from our equations were better than previously developed equations. All pLR prediction equations presented a lower accuracy compared to those developed to predict pGRF. **Conclusion:** Walking and running pGRF can be predicted with high accuracy by accelerometry-based equations, representing an easy way to determine mechanical loading in free-living conditions. The pLR prediction equations yielded an unsatisfactory accuracy. **Key Words:** ACTIVITY MONITOR, FORCE PLATES, LOCOMOTION, RAW ACCELERATION, MECHANICAL LOADING.

@@

A convenience sample of `r max(sample_size$pGRF_N)` adults (`r unname(sample_size_sex["F"])` males; `r sample_descriptives$age_mean`±`r sample_descriptives$age_sd` years; `r sample_descriptives$height_mean`±`r sample_descriptives$height_sd` cm; `r sample_descriptives$body_mass_mean`±`r sample_descriptives$body_mass_sd` kg; `r sample_descriptives$BMI_mean`±`r sample_descriptives$BMI_sd` kg·m^-2^, X̄±SD) with no self-reported neurological or musculoskeletal limitations was recruited. Height and body mass were assessed following standard procedures with a stadiometer and a digital scale, respectively. All participants were informed about the experiments purpose and protocol before giving written informed consent. The study was approved by the local Ethics Committee (CES 192-14).
